Details of specific functions

### 2020-12-03 inst/gitbook/03_specific-tutorials.Rmd
bug fix in paleo demo

## Plotting the results with some plot.dispRity arguments
plot(disparity_time_slices,
    quantiles = c(seq(from = 10, to = 100, by = 10)),
    cent.tend = sd, type = "c", elements = TRUE,
    col = c("black", rainbow(10)),
    ylab = c("Disparity", "Diversity"), chrono.subsets = FALSE,
    xlab = "Time (in in units from past to present)",
    observed = TRUE,
    main = "Many more options...")

@@

```{r}
## Ordinating the eurodist matrix
euro_ord <- cmdscale(eurodist, k = nrow(eurodist) - 2)

>>>>

## Plotting the results with some plot.dispRity arguments
plot(disparity_time_slices,
    quantiles = c(seq(from = 10, to = 100, by = 10)),
    cent.tend = sd, type = "c", elements = TRUE,
    col = c("black", rainbow(10)),
    ylab = c("Disparity", "Diversity"),
    xlab = "Time (in in units from past to present)",
    observed = TRUE,
    main = "Many more options...")

@@

```{r}
## Ordinating the eurodist matrix (with 11 dimensions)
euro_ord <- cmdscale(eurodist, k = 11)
